---
title: "Feature plots with `feature_plot2()`"
author: "scexpr"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 5
vignette: >
  %\VignetteIndexEntry{Feature plots with feature_plot2()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  warning = FALSE,
  message = FALSE
)
```

## Overview

`feature_plot2()` draws gene expression or Seurat metadata on a two-dimensional embedding from the reductions slot. Just like Seurat's built-in function. It has several opinionated defaults and features that some people may view as an improvement over Seurat's function. It accepts either one Seurat object or a (named) list of multiple Seurat objects. Two small example Seurat objects made from PBMC data sets from 10X genomics are used for demonstration.

```{r read-objects}
so1 <- readRDS(system.file("extdata", "SO_5k_pbmc_v3_RNA_none_1_800_12_small.rds", package = "scexpr"))
so2 <- readRDS(system.file("extdata", "SO_pbmc8k_RNA_none_1_900_14_small.rds", package = "scexpr"))

so1

so2

names(so1@meta.data)

names(so2@meta.data)
```

## Basic plots

```{r basic1}
# one gene; expressers are colored while non-expressers are grey
scexpr::feature_plot2(SO = so1, features = "MS4A1")

# several genes, plotted as patchwork by default
scexpr::feature_plot2(SO = so1, features = c("MS4A1", "CD3E", "CD68"))

# adjust layout
scexpr::feature_plot2(SO = so1, features = c("MS4A1", "CD3E", "CD68"), nrow_combine = 2)

# co-plot meta columns
scexpr::feature_plot2(SO = so1, features = c("MS4A1", "CD3E", "pca12_rna800_snn_res_0.1", "pct_mt"))

# do not combine by patchwork
plot_list <- scexpr::feature_plot2(SO = so1, features = c("MS4A1", "CD3E", "CD68"), combine = F)
length(plot_list)

# reduction names are matched, umap was default
scexpr::feature_plot2(SO = so1, features = "CD3E", "tsne")
scexpr::feature_plot2(SO = so1, features = "CD3E", "pca")

# increase dot size
scexpr::feature_plot2(SO = so1, features = "CD3E", pt_size = 3)

# increase dot size of expressers only
scexpr::feature_plot2(SO = so1, features = "CD3E", pt_size = 3)
```
